\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-09-22 chapters/gaze_independence.tex
Add decoders

\todo{mention partially published}
\todo{spatially vs temporally organized interfaces}
\todo{talk about covert shifts in spatial attention alpha}

\section{The gaze-dependence problem}

\todo{define eye motor issues}
\todo{systematic review of prevalences and prevalences of eye motor issues per disorder}
\todo{
cite{Guo2022}
cite{Prasad2010}
cite{Serra2018}
cite{Bogousslavsky1987}
cite{Castelnovo2016}
cite{Polet2020}
}

@@

\newcommand\fnlis{\footnote{
Multiple definitions of \ac{lis} are encountered in
BCI and neurological literature.
Some definitions include only tetraplegic patients without eye movements used
for communications.
Others distinguish Complete Locked-in Syndrome (CLIS) with full body paralysis,
including no eye motor control at all, from a \ac{lis} state with some preserved eye
movements or minor motor output.
While some definitions only include patients who suffered stroke or traumatic
brain injury to specific regions in the brain (midbrain, brainstem,
cerebellum),
it can also generally refer to the state of full body paralysis
or loss of muscle tone incurred in neurodegenerative diseases, combined with
the inability to speak, such as occurs in late stage ALS.
In clinical reality, every tetraplegic patient has their own unique set of
preserved capabilities and from an solution-oriented \ac{bci} engineering point
of view, the etiology of the symptoms can be abstracted away.
}}

Ultimately, patients with \ac{lis} from one of the main
\ac{bci}.
In this work, we'll define \ac{lis} patients as those a situation of (near)
complete paralysis and difficulties or the inability to communicate without
assistive technology, combined with severe or complete eye motor
impairment\fnlis.
\todo{from a solution engineering point of view, the etiology does not matter that
much}.
\todo{fill out which definition we use, wolpaw criteria}
\todo{cite studies per pathology}
\todo{check definition in Wolpaw\&Wolpbaw Brain-Computer Interfaces: Principles
and Practice}
\Ac{lis} patients are are (nearly) completely paralyzed and have
effort communicating without assistive technology.

Traditional visual BCI scenarios require the user to overtly direct their
visuospatial attention (VSA) and gaze toward the screen target they intend to select.
In most settings, screen targets are overlaid with non-overlapping, transient
stimuli that evoke event-related EEG potentials (ERPs).
The selected target can be decoded from these ERPs, as is the case for the
oddball paradigm where observing a rare but attended stimulus evokes a P3 ERP
component.
However, a critical challenge arises when users rely solely or in part on covert
VSA, which involves directing visuospatial attention without corresponding eye gaze.
In these cases, classical solutions often fall short of the widely accepted
80\% target selection accuracy threshold deemed necessary for a comfortable user
experience~\cite{Brunner2010,Frenzel2011,Treder2010,Ron2019,Neeling2019},
calling for alternative, gaze-independent solutions.

@@

\section{Gaze-independent BCI paradigms}
\label{sec:gaze-independence-paradigms}
Gaze-independent ERP-based BCIs~\cite{Riccio2012, Aloise2012} can be realized in three
ways. Firstly, non-visual stimulation paradigms such as auditory and somatosensory paradigms
do not rely on gaze redirection but often result in lower information transfer
rates, increased mental effort and user-dependent variability~\cite{Reichert2020b}.
\todo{insert table from riccio in text as numbers, not as table}
\todo{true for non-invasive}

Secondly, visual stimulation can be optimized, e.g. such that the stimuli are always
present in the field of view either overtly~\cite{Acqualagna2013, Won2018,
Lin2018} or covertly~\cite{Treder2010,Pires2011,Lees2018}. Some noteworthy examples include the GIBS Block Speller~\parencite{Pires2011},
the GeoSpell interface~\parencite{Aloise2012}, and the RSVP
speller~\parencite{Acqualagna2011}.
Non-spatial visual attention (feature attention) can also be exploited, such as
attention to stimulus color, shape or symbol~\cite{Zhang2010,Treder2011,Hwang2015}.
Alternative visual stimulation paradigms can modulate specific ERP components
that are more sensitive to stimulation in the visual periphery~\cite{Schaeff2012,Xu2022}.
Nevertheless, these methods, can suffer too from reduced information
transfer rates~\cite{Chennu2013}.
Furthermore, these systems typically require users to focus on a central fixation point while
selecting peripheral targets.
This entails that they still rely to some extent on
eye motor control, often necessitating central gaze fixation.
\todo{advantages disadvantages rewrite (requires gaze fixation, low itr, not tested with split attention)}
\todo{
Firstly, by avoiding visual
stimulation entirely and opting for auditory or somatosensory stimulation instead.
However, these alternatives often result in lower information transfer rates,
increased mental effort and variable outcomes for different users.
Secondly, gaze-independence can
be achieved by adapting the interface to display stimuli such that they
are always in the center of the field of view, by exploiting visual
non-spatial attention (feature attention), or a combination thereof.
These interfaces suffer equally from reduced information transfer rates.
}

Thirdly, stimuli can be presented in a standard BCI paradigm, but visuospatial attention
can be decoded separately from gaze direction.
Earlier work has made advances in decoding lateralized covert
VSA harnessing the N2pc ERP component~\cite{Thiery2016,Reichert2020b,Wang2022},
decoding covert VSA shifts from spectral content~\cite{Tonin2013}, or hybrid
stimulation paradigms~\cite{Egan2017}.
Since these methods often require a slower stimulation pace than the classical
ERP BCI paradigm, gaze-independent decoding in fast-paced ERP paradigm stimulation
remains underexplored.
\cite{Aloise2012b} aimed to bridge the performance gap between covert and
overt VSA decoding performance.
They compared classical linear and non-linear ERP classifiers on a covert
attention P3 ERP component dataset.
The results revealed no significant performance improvement in covert VSA
decoding for any of the investigated decoders.
\cite{Arico2014} observed higher variability in single-trial P3 peak
latencies relative to stimulus onset during covert VSA compared to overt VSA.
This latency variability contributes to reduced covert VSA decoding performance.
While they proposed an analysis and performance prediction method, they did not provide a
decoding solution.
They suggested that compensating for latency jitter could enhance covert VSA
decoding, but did not actually verify this hypothesis directly.
Additionally, \cite{hardiansyah2020single} developed a classifier for
covert VSA ERPs, exploiting single-trial latency features in combination with
amplitude features for classification with a support vector machine.
They demonstrated the positive influence of single-trial ERP component latency
features on covert VSA inference yet did not attempt to correct the amplitude
features for these latencies.
\todo{Should we already mention Frenzel here?}
\cite{Frenzel2011} introduced a similar protocol to our split VSA
setting.
They showed that it is possible to perform split VSA and that, in this
case, visuospatial attention and gaze direction can separately be decoded using
classical ERP techniques.
To the best of our
knowledge, this is the sole study that investigated split attention in ERP-based BCIs.
However, \cite{Frenzel2011} considered their interface only for the case
where the user actively intends to select both targets determined by the gaze
and the VSA.
In the split VSA setting considered in our work, we rather instruct the participant to ignore
the distractor and only attend the cued target, since we are interested in
decoding the visuospatial attention only.

P3 latency generally falls between 350ms and 600ms~\cite{Luck2014}, but this
value is heavily dependent on the subject and the task, and can vary from trial
to trial~\cite{Ouyang2017}.
The work of \cite{Arico2014}
illustrates that the variation in single-trial P3 latencies is important in
gaze-independent decoding and has been hampering covert VSA decoding performance.
In this work we aim to reprise their hypothesis stating that jitter compensation improves
covert VSA performance and extend it by developing a decoder and evaluating it
in a broader range of gaze-independent settings, including split VSA.
\todo{Check connection}

\todo{provisionary doctoral plan}
\todo{check WIP seminar}
\todo{update text}

@@

The general goal of this PhD is to tackle the gaze-dependence in visual BCIs.
\todo{refer to ITRs from previous chapter}
Section{sec:gaze-independence-paradigms} showed that visual BCI paradigms form
a good candidate for a performant gaze-independent BCI.
While the central gaze fixation of most visual gaze-independent paradigms still
relies to some extent on eye motor control, we aim to circumvent this.
We make a distinction here between spatially organized interfaces, where
multiple targets are displayed at the same time at different spatial locations,
and temporally organized interfaces, like Rapid Serial Visual Presentation,
where targets or small sets of targets are shown consecutively.
Traditionally, spatially organized interfaces have a higher information transfer
rate, but are also more gaze-dependent than temporally organized interfaces.
In such an interface, stimuli can be presented in a standard BCI paradigm, but
visuospatial attention can be decoded separately from the position of gaze,
which do not necessarily need to coincide.

This leads us to adopt a specific approach: improve the performance of a
spatially organized visual oddball ERP-based brain
computer interface by using a suited decoding strategy.
Hence, our working hypothesis is as follows:
\begin{quote}
	\textit{A spatially organized visual oddball ERP BCI with a suited decoder
		can achieve similar or higher information transfer rate in patient
		populations with eye motor deficits than other
		gaze-independent alternatives described in literature.}
\end{quote}
\todo{tone this down a bit to what can be proven}

@@

\todo{\emph{Goal:} Enable communication for eye-motor impaired patients}
\todo{\emph{Method:} Design a comfortable interface that allows them to maximally exploit
their residual gaze capabilities, by leveraging a non-invasive high-ITR
visuospatial ERP-based BCI and improving ERP decoding performance (in general
and specifically in gaze-independent settings).}

@@

\todo{Overt, covert, split, free, illustration from poster}
\todo{clear definitions}

@@

\todo{Classifier-based Latency Estimation with Woody iterations}
Literature shows that better covert attention performance can be achieved by
counteracting the non-stationarity of the P3 ERP component in covert
attention settings~\cite{Arico2014}.
This can be done by estimating the latency of each single-trial ERP and aligning
the P3 peaks to all fall at the same moment.
The resulting aligned data and the set of latencies can then be used to train a
classifier that is more robust to jitter.

@@

\subsection{Experiments}
\todo{Healthy participant study}
We designed a visual oddball interface that helps us study and adapt
to the effects of eye motor impairment on the ERP, when using existing state-of-the-art
decoders and on our own proposed decoders.
In a first series of experiments, we recorded data with this interface from healthy participants.
The goal of these experiments is to benchmark
gaze-independent ERP decoding algorithms.
We denote this dataset as the Covert Visuospatial Attention ERP dataset
(CVSA-ERP)
This study was approved by the Ethics Commission of University Hospital Leuven
(S62547).

Using a hexagonal lay-out interface, similar to the visual Hex-o-Spell proposed
by Treder \& Blankertz~\cite{Treder2010}, we present six flashing targets (without letters or
symbols) to the participant while the EEG and electro-oculogram (EOG) are
recorded, as well as eye gaze using eye tracking.
To simulate the dissociation between the eye gaze (visual attention) and the
intended target (mental attention) which could occur in patients with hampered eye
motor control, healthy participants are cued to operate the BCI in specific
visuospatial attention (VSA) conditions.
Each subject performs 5 different VSA conditions as illustrated in
Figure~\ref{fig:vsa-conditions}.
\todo{do we already want this here?}
\begin{figure}
	%\includegraphics[width=\linewidth]{figures/attention_modes.eps}
	\caption{Visuospatial attention (VSA) conditions in our experiment. The user is
		asked to dissociate their visual and mental attention by gazing at a
		crosshair while attending a target, depending on the prompted condition.}%
	\label{fig:vsa-conditions}
\end{figure}
\todo{new picture that shows more clearly a user operating freely where they
can gaze}
In the overt case, subjects are instructed to gaze at the cued
target they are also mentally attending; in the covert case, subjects are instructed
to gaze at the center of the screen while mentally attending to the cued target.
Finally, we introduce a VSA condition that is understudied in the context of
gaze-independent BCI development: split VSA.
In split VSA, the participant mentally focuses on one cued target while gazing at
another (the distractor).
Depending on the inter-target distance along the hull of the hexagon between the
attended target and the distractor we discern three split VSA subconditions:
the distractor is either clockwise or counterclockwise directly next to the
attended target ($d=1$), there is one other target between the attended target and
the distractor ($d=2$), or the distractor is opposite the intended target
($d=3$).

After data collection from healthy participants and decoder development, we
will carry out a patient study using a similar interface.
The goal of the patient study is to evaluate the influence of eye motor
deficits in patient populations on existing state-of-the-art decoders and on
our proposed decoding methods.
\todo{update with current results}

\todo{Patient study}
\todo{refer to chapters}

>>>>

\emph{Parts oare dissociated in the
Section~\ref{sec:gaze-independence} have been published in
\textcite{VanDenKerchove2024}.}

\todo{spatially vs temporally organized interfaces}
\todo{talk about covert shifts in spatial attention alpha}

\section{The gaze-dependence problem}
\label{sec:gaze-dependence}

\todo{define eye motor issues}

@@

\newcommand\fnlis{\footnote{
Multiple definitions of \ac{lis} are encountered in
BCI and neurological literature.
Some definitions include only tetraplegic patients without eye movements used
for communications.
Others distinguish Complete Locked-in Syndrome (CLIS) with full body paralysis,
including no eye motor control at all, from a \ac{lis} state with some preserved eye
movements or minor motor output.
While some definitions only include patients who suffered stroke or traumatic
brain injury to specific regions in the brain (midbrain, brainstem,
cerebellum)~\cite{Smith2005},
it can also generally refer to the state of full body paralysis
or loss of muscle tone incurred in neurodegenerative diseases, combined with
the inability to speak, such as occurs in late stage ALS.
In clinical reality, every tetraplegic patient has their own unique set of
preserved capabilities and from an solution-oriented \ac{bci} engineering point
of view, the etiology of the symptoms can be abstracted away.
}}

\newcommand\fnwolpawcrit{\footnote{
\it``The first class consists of people who are truly totally locked-in (e.g.,
due to end-stage ALS or severe cerebral palsy), who have no remaining
useful neuromuscular control of any sort, including no eye movement.
\elide\ This class is very small. \elide\
The second class of potential BCI users comprises those who retain
a very limited capacity for neuromuscular control. This group includes
people who retain some useful eye movement or enough limb muscle
function to operate a single-switch system. Such control is often slow,
unreliable, or easily fatigued.
This group is much larger than the first.
\elide\
The third class of potential BCI users, which is the largest of all,
includes those who still retain (and can be expected to continue to
retain) substantial neuromuscular control, particularly speech and/or
hand control, and can, therefore, operate a wide range of assistive com-
munication and control devices.''
}}

Together, some of these patients constitute the \ac{lis} patient group, which
forms one of the main \ac{bci} target populations.
In this work, we'll define \ac{lis} patients as those a situation of (near)
complete paralysis and difficulties or the inability to communicate without
assistive technology, corresponding corresponds to classes one and two defined by
\textcite{Wolpaw2006}\fnwolpawcrit.
Additionally some degree of severe or complete eye motor impairment is ususally
necessary to qualify as locked-in\fnlis.
Since this work is concerned with gaze-impaired patients, we will adopt this
interpretation.
Case study reports~\cite{Patterson1986} show that the population of locked-in
patients with complete eye motor paralysis is very small.
Hence, it would be interesting to focus efforts in \ac{bci} development on the
larger population of \ac{lis} patients that  currently slip through the cracks
of the current assistive technology offer.
These are the patients that require assistance to communicate independently,
which is crucial to retaining an acceptable quality of life, but whose severe
eye motor impairment prevents them from using eye tracking based solutions.

\todo{order of concepts in next two paragraphs can be tweaked}
This leads us to what we'll call the \emph{gaze-dependence problem in visual
BCI}:
Traditional visual BCI scenarios require the user to overtly direct their both
\ac{vsa} and gaze toward the screen target they intend to select.
For our purposes, screen targets are overlaid with non-overlapping, transient
stimuli that evoke event-related  potentials \acp{erp} in the \ac{eeg}.
The selected target can be decoded from these \acp{erp}, as is the case for the
oddball paradigm where observing a rare but attended stimulus evokes a P3 ERP
component.
However, a critical challenge arises when users rely solely or in part on covert
VSA, which involves directing visuospatial attention without corresponding eye gaze.
In these cases, classical solutions often fall short of the widely accepted
80\% target selection accuracy threshold~\cite{Brunner2010,Frenzel2011,Treder2010,Ron2019} deemed necessary for a comfortable user
experience~\cite{Neeling2019}, calling for alternative, gaze-independent
solutions.

@@

\section{Gaze-independent BCI paradigms}
\label{sec:gaze-independence}

Gaze-independent ERP-based BCIs~\cite{Riccio2012, Aloise2012} can be realized in three
ways.
Firstly, active BCI communication paradigms relying on endogenous activation from the user
do not rely on sensory stimulation.
Examples of this are imagined movement or imagined speech paradigms.
These paradigms can yield very high information transfer
rates~\cite{Willett2021,Metzger2023}, both due to their intuitiveness and the
complexity that can be captured in commands, but often only do so when paired
with invasive recording.
Non-visual reactive paradigms that use e.g. auditory and somatosensory
stimulation do not rely on gaze redirection exist but also result in lower information transfer
rates compared to visual paradigms.
Furthermore, they can suffer from increased mental effort in operation and user-dependent variability~\cite{Reichert2020b}.
\todo{insert table from riccio in text as numbers, not as table}

Secondly, current visual stimulation paradigms can be optimized, e.g. such that
the stimuli are always present in the field of view either overtly~\cite{Acqualagna2013, Won2018,
Lin2018} or covertly~\cite{Treder2010,Pires2011,Lees2018}. Some noteworthy examples include the GIBS Block Speller~\parencite{Pires2011},
the GeoSpell interface~\parencite{Aloise2012}, and the RSVP
speller~\parencite{Acqualagna2011}.
Non-spatial visual attention (feature attention) can also be exploited, such as
attention to stimulus color, shape or symbol~\cite{Zhang2010,Treder2011,Hwang2015}.
Alternative visual stimulation paradigms can modulate specific ERP components
that are more sensitive to stimulation in the visual periphery~\cite{Schaeff2012,Xu2022}.
Nevertheless, these methods, can suffer too from reduced information
transfer rates~\cite{Chennu2013}.
Furthermore, these systems typically require users to focus on a central fixation point while
selecting peripheral targets.
This entails that they still rely to some extent on
eye motor control, often necessitating central gaze fixation.
\todo{advantages disadvantages rewrite (requires gaze fixation, low itr, not tested with split attention)}

Thirdly, stimuli can be presented in a standard BCI paradigm, but visuospatial
attention can be decoded separately from gaze direction.
\cite{Aloise2012b} aimed to bridge the performance gap between covert and
overt VSA decoding performance.
They compared classical linear and non-linear ERP classifiers on a covert
attention P3 ERP component dataset.
The results revealed no significant performance improvement in covert VSA
decoding for any of the investigated decoders.
More recent work has made advances in decoding lateralized covert
VSA harnessing the N2pc ERP component~\cite{Thiery2016,Reichert2020b,Wang2022},
decoding covert VSA shifts from spectral content~\cite{Tonin2013}, or hybrid
stimulation paradigms~\cite{Egan2017}.
Since these methods often require a slower stimulation pace than the classical
ERP BCI paradigm, gaze-independent decoding in the fast-paced reactive ERP paradigm
leveraging spatial attention remains underexplored.

\todo{check funding proposal}
\todo{check provisional doctoral plan}
\todo{check WIP seminar}

@@

The general goal of this PhD is to tackle the gaze-dependence in visual BCIs.
\todo{refer to ITRs from previous chapter}
Section{sec:gaze-independence} showed that visual BCI paradigms form
a good candidate for a performant gaze-independent BCI.
While the central gaze fixation of most visual gaze-independent paradigms still
relies to some extent on eye motor control, we aim to circumvent this.
We make a distinction here between spatially organized interfaces, where
multiple targets are displayed at the same time at different spatial locations,
and temporally organized interfaces, like Rapid Serial Visual
Presentation\todo{cite},
where targets or small sets of targets are shown consecutively.
Traditionally, spatially organized interfaces have a higher information transfer
rate, but are also more gaze-dependent than temporally organized interfaces.
In such an interface, stimuli can be presented in a standard BCI paradigm, but
visuospatial attention can be decoded separately from the position of gaze,
which do not necessarily need to coincide.

This leads us to adopt a specific approach: improve the performance of a
spatially organized visual oddball ERP-based brain
computer interface by using a suited decoding strategy.
Hence, our working hypothesis is as follows:
\begin{quote}
	\textit{A spatially organized visual oddball ERP BCI with a suited decoder
		can achieve a similar transfer rate in patient
		populations with eye motor deficits than other gaze-independent alternatives
    described in literature.}
\end{quote}

@@

This specific hypothesis is embedded within a broader goal of enabling
effective communication for eye-motor impaired \ac{lis} patients.
Ultimately, we wish to design a comfortable interface that allows them to maximally exploit
their residual gaze capabilities, by leveraging a non-invasive, high-\ac{itr}
BCI on the one hand, and on the other hand improving \ac{erp} decoding performance
in general.

@@

\todo{mention, free, split, frenzel}
\todo{Overt, covert, split, free, illustration from poster}
\todo{clear definitions, table from paper}

First, we designed a visual oddball interface that helps us study and adapt
to the effects of eye motor impairment on the ERP, when using existing state-of-the-art
decoders and on our own proposed decoders.
Using a hexagonal lay-out interface, similar to the visual Hex-o-Spell proposed
\textcite{Treder2010}, we present six flashing circular targets
(without letters or symbols) to the participant while the EEG and
electro-oculogram (EOG) are recorded, as well as eye gaze using eye tracking.

The interface can be operated in different VSA conditions as illustrated in
Figure~\ref{fig:gaze-vsa}.
\fourpanefig
  {\figpane{figures/gaze_independence/attention_overt.eps}{
    \emph{Overt \ac{vsa}}.
    Gaze and \ac{vsa} coincide on a target.}{fig:gaze-vsa-overt}}
  {\figpane{figures/gaze_independence/attention_covert.eps}{\emph{Covert
  \ac{vsa}}.
  Gaze rests on the center of the screen, while \ac{vsa} is directed towards a
  target.}{fig:gaze-vsa-covert}}
  {\figpane{figures/gaze_independence/attention_split.eps}{
    \emph{Split \ac{vsa}}. \ac{vsa} is directed towards a target, while the
    gaze rests on another.}{fig:gaze-vsa-split}}
  {\figpane{figures/gaze_independence/attention_free.eps}{\emph{Free \ac{vsa}}.
  The user is free to direct their gaze as they deem most comfortable
  All previous \ac{vsa} conditions are possible.}{fig:gaze-vsa-free}}
  {\Ac{vsa} conditions defined in our hexagonal spatial \ac{erp} paradigm interface.}
  {fig:gaze-vsa}

In the overt case, users gaze at the cued
target they are also mentally attending; in the covert case, users
gaze at the center of the screen while mentally attending to the cued target.
Finally, we introduce a VSA condition that is understudied in the context of
gaze-independent BCI development: split VSA.
In split VSA, the user mentally focuses on one cued target while gazing at
another (the distractor).

The option to dissociate gaze and visuospatial attention will allow us to
investigate the effect of gaze control on \ac{bci} performance.

@@

\todo{Classifier-based Latency Estimation with Woody iterations}

P3 latency generally falls between 350ms and 600ms~\cite{Luck2014}, but this
value is heavily dependent on the subject and the task, and can vary from trial
to trial~\cite{Ouyang2017}.
The work of \cite{Arico2014} illustrates that the variation in single-trial P3
latencies is important in gaze-independent decoding and has been hampering covert
VSA decoding performance.
In this work we aim to reprise their hypothesis stating that jitter compensation improves
covert VSA performance and extend it by developing a decoder and evaluating it
in a broader range of gaze-independent settings, including split VSA.

\todo{check overlap}

Literature shows that better covert attention performance can be achieved by
counteracting the non-stationarity of the P3 ERP component in covert
attention settings~\cite{Arico2014}.
This can be done by estimating the latency of each single-trial ERP and aligning
the P3 peaks to all fall at the same moment.
The resulting aligned data and the set of latencies can then be used to train a
classifier that is more robust to jitter.

@@

\subsection{Experiments}

\todo{Healthy participant study}
In a first series of experiments, we recorded data with this interface from healthy participants.
The goal of these experiments is to benchmark
gaze-independent ERP decoding algorithms.
We denote this dataset as the Covert Visuospatial Attention ERP dataset
(CVSA-ERP)
This study was approved by the Ethics Commission of University Hospital Leuven
(S62547).
To simulate the dissociation between the eye gaze (visual attention) and the
intended target (mental attention) which could occur in patients with hampered eye
motor control, healthy participants are cued to operate the BCI in specific
\ac{vsa} conditions.

\todo{mention multi-center patient study case studies in cooperation
After data collection from healthy participants and decoder development, we
will carry out a patient study using a similar interface.
The goal of the patient study is to evaluate the influence of eye motor
deficits in patient populations on existing state-of-the-art decoders and on
our proposed decoding methods.
}
\todo{update with current results}

\todo{refer to chapters}
